---
title: "Jin_Silvia_hw4"
author: "Silvia Jin"
date: "October 6, 2016"
output: pdf_document
---

### Problem 01
a) Create the vector (1,2,3,...,19,20).

```{r}
1:20
```

b) Create the vector (20,19,...,2,1).

```{r}
c(1:20,19:1)
```
c) Create the vecotr (1,2,3,...,19,20,19,18,...,2,1).
```{r}
c(1:20,19:1)
```

d) Create the vector (4,6,3) and assign it to the name tmp.
```{r}
tmp <- c(4,6,3)
tmp
```

e) Create the vector (4,6,3,4,6,3,...,4,6,3) where there are 10 occurrences of 4.
```{r}
rep(c(4,6,3),10)
```

f) Create the vector (4,6,3,4,6,3,...,4,6,3,4) where there are 11 occurrences of 4.
```{r}
rep(c(4,6,3),l=31)
```

g) Create the vector(4,4,...,4, 6,6,...,6, 3,3,...,3) where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
```{r}
rep(c(4,6,3), times = c(10,20,30))
```

### Problem 02
Create a vecotr of the values of e^x cos(x) at x = 3,3.1,3.2,...,5.9,6.

First we create a sequence of x, from 3 to 6, with steps of 0.1, then we calculate the equation of each entry in the list.
```{r}
xs <- seq(3,6,0.1)
vec02 <- exp(xs)*cos(xs)
vec02
```


### Problem 03
a) Create the vector $(0.1^3*0.2^1, 0.1^6*0.2^4,...,0.1^{36}*0.2^{34})$.

First we create the two sequences of the exponents, then we calculate the whole sequence.
```{r}
exp01 <- seq(3,36,3)
exp02 <- seq(1,34,3)
vec03a <- (0.1^exp01) * (0.2^exp02)
vec03a
```

b) Create the vector (2,2^2/2,2^2/3,...,2^25/25).

First we create the vector for the exponents (exps), then we create the vector for the numerator (nums) and for the denominator (den), then we calculate the result (vec03b).
```{r}
exps <- seq(1,25)
nums <- 2^exps
den <- seq(1,25)
vec03b <- nums/den
vec03b
```

### Problem 04

a) 

First we initialize a value (ans04a) for the sum, then we use a for loop to add up the sum.
```{r}
ans04a <- 0
for (i in seq(10,100)){
  ans04a <- ans04a + i^3 + 4*i^2
}
ans04a
```
Note: for this problem, we could also use:
```{r}
tmp <- 10:100
sum(tmp^3+4*tmp^2)
```

b) 

First we initialize a value (ans04b) for the sum, then we use a for loop to add up the sum.
```{r}
ans04b <- 0
for (i in seq(1,25)){
  ans04b <- ans04b + (2^i)/i + (3^i)/(i^2)
}
ans04b
```

Note: for this problem, we could also use:
```{r}
tmp <- 1:25
sum((2^tmp)/tmp+(3^tmp)/(tmp^2))
```

### Problem 05

a) Create the character vector ("label 1", "label 2",...,"label 30").
```{r}
paste("label", 1:30, sep = " ")
```

b) Create the character vector ("fn1", "fn2",...,"fn30").
```{r}
paste("fn", 1:30, sep="")
```

### Problem 06

g) Create the vector(4,4,...,4, 6,6,...,6, 3,3,...,3) where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
```{r}
rep(c(4,6,3), times = c(10,20,30))
```

