---
title: "Jin_Silvia_hw4"
author: "Silvia Jin"
date: "October 6, 2016"
output: html_document
---

### Problem 01
a) Create the vector $(1,2,3,...,19,20)$.

```{r}
1:20
```

b) Create the vector $(20,19,...,2,1)$.

```{r}
20:1
```

c) Create the vecotr $(1,2,3,...,19,20,19,18,...,2,1)$.
```{r}
c(1:20,19:1)
```

d) Create the vector $(4,6,3)$ and assign it to the name tmp.
```{r}
tmp <- c(4,6,3)
tmp
```

e) Create the vector $(4,6,3,4,6,3,...,4,6,3)$ where there are 10 occurrences of 4.
```{r}
rep(c(4,6,3),10)
```

f) Create the vector $(4,6,3,4,6,3,...,4,6,3,4)$ where there are 11 occurrences of 4.
```{r}
rep(c(4,6,3),l=31)
```

g) Create the vector $(4,4,...,4, 6,6,...,6, 3,3,...,3)$ where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
```{r}
rep(c(4,6,3), times = c(10,20,30))
```

### Problem 02
Create a vecotr of the values of $e^x cos(x)$ at $x = 3,3.1,3.2,...,5.9,6$.

First we create a sequence of x, from 3 to 6, with steps of 0.1, then we calculate the equation of each entry in the list.
```{r}
xs <- seq(3,6,0.1)
vec02 <- exp(xs)*cos(xs)
vec02
```


### Problem 03
a) Create the vector $(0.1^3*0.2^1, 0.1^6*0.2^4,...,0.1^{36}*0.2^{34})$.

First we create the two sequences of the exponents, then we calculate the whole sequence.
```{r}
exp01 <- seq(3,36,3)
exp02 <- seq(1,34,3)
vec03a <- (0.1^exp01) * (0.2^exp02)
vec03a
```

b) Create the vector $(2,2^2/2,2^2/3,...,2^{25}/25)$.

First we create the vector for the exponents (exps), then we create the vector for the numerator (nums) and for the denominator (den), then we calculate the result (vec03b).
```{r}
exps <- seq(1,25)
nums <- 2^exps
den <- seq(1,25)
vec03b <- nums/den
vec03b
```

### Problem 04

a) Calculate the sum $\sum^{100}_{i=10}(i^3+4i^2)$.

First we initialize a value (ans04a) for the sum, then we use a for loop to add up the sum.
```{r}
ans04a <- 0
for (i in seq(10,100)){
  ans04a <- ans04a + i^3 + 4*i^2
}
ans04a
```

Note: for this problem, we could also use:
```{r}
tmp <- 10:100
sum(tmp^3+4*tmp^2)
```

b) Calculate the sum $\sum^{25}_{i=1}(\frac{2^i}{i}+\frac{3^i}{i^2})$.

First we initialize a value (ans04b) for the sum, then we use a for loop to add up the sum.
```{r}
ans04b <- 0
for (i in seq(1,25)){
  ans04b <- ans04b + (2^i)/i + (3^i)/(i^2)
}
ans04b
```

Note: for this problem, we could also use:
```{r}
tmp <- 1:25
sum((2^tmp)/tmp+(3^tmp)/(tmp^2))
```

### Problem 05

a) Create the character vector ("label 1", "label 2",...,"label 30").
```{r}
paste("label", 1:30, sep = " ")
```

b) Create the character vector ("fn1", "fn2",...,"fn30").
```{r}
paste("fn", 1:30, sep="")
```

### Problem 06

Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers $0,1,...,999$. Both vectors have length 250.

```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
```

a) Create the vector $(y_2-x_1,...,y_n-x_{n-1})$.

First we create a null vector, then we use a for loop to put in each value.
```{r}
vec06a <- numeric()
for (i in seq(1,length(xVec)-1)){
  vec06a[i] <- yVec[i+1] - xVec[i]
}
vec06a
```

Note: for this problem, we could also use:
```{r}
yVec[-1] - xVec[-length(xVec)]
```

b) Create the vector $(sin(y1)/cos(x2),sin(y2)/cos(x3),...,sin(y_{n-1)}/cos(x_n))$.

First we create a null vector, then we use a for loop to put in each value.
```{r}
vec06b <- numeric()
for (i in seq(1,length(xVec)-1)){
  vec06b[i] <- sin(yVec[i])/cos(xVec[i+1])
}
vec06b
```

c) Create the vector $(x_1+2x_2-x_3,x_{n-2}+2x_{n-1}-x_n)$.

First we create a null vector, then we use a for loop to put in each value.
```{r}
vec06c <- numeric()
for (i in seq(1,length(xVec)-2)){
  vec06c[i] <- xVec[i]+2*xVec[i+1]-xVec[i+2]
}
vec06c
```

d) Calculate the sum $\sum^{n-1}_{i=1}\frac{e^{-x_i}+1}{x_i+10}$.

First we create an initial value (ans10d), then we use a for loop to add up the values.
```{r}
ans06d <- 0
for (i in seq(1,length(xVec)-1)){
  ans06d <- ans06d +exp(-xVec[i+1])/(xVec[i]+10)
}
ans06d
```

### Problem 07

This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.

a) Pick out the values in yVec which are $>600$.

First we create a null vector (ans07a), then we use a for loop to put in each value.
```{r}
ans07a <- numeric()
for (num in yVec){
  if (num > 600){
    ans07a <- c(ans07a, num)
  }
}
ans07a
```

Note: for this problem, we could also use:
```{r}
yVec[yVec>600]
```

b) Get the index position in yVec of the values which are $>600$.

First we create a null vector (ans07b), then we use a for loop to put in each value.
```{r}
ans07b <- numeric()
for (i in seq(1,length(xVec))){
  if (xVec[i]>600){
    ans07b <- c(ans07b,i)
  }
}
ans07b
```

c) Get the values in xVec which correspond to the values in yVec which are $> 600$. (By correspond, we mean at the same index positions.)

First we create a null vector (ans07c), then we use a for loop to put in each value.
```{r}
ans07c <- numeric()
for (i in seq(1,length(yVec))){
  if (yVec[i]>600){
    ans07c <- c(ans07c,xVec[i])
  }
}
ans07c
```

Note: for this problem, we could also use:
```{r}
xVec[yVec>600]
```

d) Create the vector $(|x_1-\bar{x}|^{1/2},|x_2-\bar{x}|^{1/2},...,|x_n-\bar{x}|^{1/2})$ where $\bar{x}$ denotes the mean of the vectors $x=(x_1,x_2,...,x_n)$.

First we calculate the mean of xVec, then we create the vector.
```{r}
xMean <- mean(xVec)
ans07d <- sqrt(abs(xVec-xMean))
ans07d
```

Note: for this problem, we could also use:
```{r}
sqrt(abs(xVec-mean(xVec)))
```

e) How many values in yVec are within 200 of the maximum value of the terms in yVec? 

First we create an initial value (ans07e), then we use a for loop to add up the values.
```{r}
yMax <- max(yVec)
ans07e <- 0
for (num in yVec){
  if (num > yMax-200){
    ans07e <- ans07e + 1
  }
}
ans07e
```

Note: for this problem, we could also use:
```{r}
sum(yVec>max(yVec)-200)
```

f) How many numbers in xVec are divisible by 2? (Note that the mod operator is denoted \%\%.)

First we create an initial value (ans07f), then we use a for loop to add up the values.
```{r}
ans07f <- 0
for (num in xVec){
  if (num%%2 == 0){
    ans07f <- ans07f + 1
  }
}
ans07f
```

Note: for this problem, we could also use:
```{r}
sum(xVec%%2==0)
```

g) Sort the numbers in the vector xVec in the order of increasing values in yVec

First we sort the values in yVec, and store the sorted indexes, and create a null vector (ans07g), then we put in the x values corresponding to the indexes using a for loop.
```{r}
indexes <- sort(yVec, index.return=TRUE)$ix
ans07g <- numeric()
for (index in indexes){
  ans07g <- c(ans07g,xVec[index])
}
ans07g
```

h) Pick out the elements in yVec at index positions $1,4,7,10,13,…$

First we create a null vector (ans07h), then we use a for loop to put in each value.
```{r}
ans07h <- numeric()
for (i in seq(1,250,3)){
  ans07h <- c(ans07h,yVec[i])
}
ans07h
```

Note: for this problem, we could also use:
```{r}
yVec[c(T,F,F)]
```

### Problem 08

Calculate

We create two vectors for the numerators (num08) and denominators (den08). Then we create an initial value (ans08) as 1, then we use a for loop to add on the values.

```{r}
num08 <- cumprod(seq(2,38,2))
den08 <- cumprod(seq(3,39,2))
ans08 <- 1
for (i in seq(1,19)){
  ans08 <- ans08 + num08[i]/den08[i]
}
ans08
```

Note: for this problem, we could also use:
```{r}
1+sum(cumprod(seq(2,38,2)/seq(3,39,2)))
```